A Case Study in Preserving a High Energy Physics Application

### 2014-01-08 paper.tex
add table

\documentclass{article}
\usepackage{multicol}
\onecolumn
\begin{document}
\title{A Case Study in Preserving a High Energy Physics Application}
\author{Haiyan Meng\\ Department of Computer Science and Engineering\\ University of Notre Dame}
\date{January 2014}
\maketitle

@@

\section{First solution to repeat the program}
First, Matthias introduced the general workflow of his tau analysis through one long email including notes, linux shell commands, web links.\\

@@

what’s more, step 3 of this tau analysis requires the new user owning the access authority for grid, however, granting  everyone who wants to repeat the analysis the access authority for grid (grid certificate) is too wasteful and unsafe.\\

\section{second solution to repeat the program}
to make the repeat of one analysis convenient and feasible, we integrate the content of all the notes, commands and web links involved in the emails into one neat, complete shell script, which begins with the definition of environment variables, then data obtainance from grid, software obtainance from cmssw, git and other web resources, and software installation, ends with the execution of the actual analysis program.\\

@@

\section{third solution to repeat the program}
the difficulty of data access authority obtainance enforces us to find out one independent solution, in which the repeat of the original analysis can be done without any external dependency. that is, one independent and self-contained package containing all the data and software dependencies is necessary.\\

parrot is a virtual filesystem access tool which attaching existing programs to a variety of remote i/o systems including http, ftp, gridftp, irods, hdfs, xrootd, grow and chirp. it traps all system calls of one program through ptrace debugging interface, and replaces them with remote i/o operations as desired. through executing one program under parrot, all the paths of files involved in this program can be recorded.\\

@@

@@

need to complement: explain the dir structure of the package:  directory ; file content + metadata; only file metadata; different process solutions\\

@@

/ /tmp/package1-4
/tmp/package1-4 /tmp/package1-4
/dev /dev
/misc /misc
/net /net
/proc /proc
/sys /sys
/var /var
/selinux /selinux

need to complement: re-execute process: re-execution process will redirect all the data access into the package except for data under proc sys dev selinux\\

@@

\section{fourth solution to repeat the program}
to integrate the data and software from multiple analysis programs into one package, the concrete information of data and software, such as size, version, source and the number of files, need to be recorded. we also need to design one more instructive shell script format, in which the data dependencies and software dependencies can be clearly expressed and recognized. the packaging process needs to be re-organized. packaging utility needs to maintain one list of current software and data subset already stored in the package. when one user wants to generate one package, it will fork the packaging utility, the packaging utility will scan the script, get the data dependency part and software dependency part, judge whether each dependency has been inside the package, and only add the new data and software into the package, and update the package information and package retrieval information.\\

@@

maybe one lightweight database like sqlite, can be used to manage the metadata of data and software. \\

difficulties: for parrot, how to recognize the start and end points of one dataset or one software. because up till now, the process unit of parrot is one single file, rather one single package.\\

questions: how to set the unit of parrot: file or package\\

the 4th version of script (how to design the new script still needs consideration):\\

\section{the relationship of different solutions}

@@

potential risk: different analysis programs share some common file names, but with different file contents. we should analyze the possibility of conflict: data.\\

in the fourth version, let user to mark whether they change the data and software. if changed, one new package is generated to avoid data overlap and pollution. otherwise, directly starts packaging process based on the current target package. \\

\section{comparison of the 2nd solution and the 3rd solution}
\subsection{the breakdown of execution time of the second solution: }
according to the table, about half of the total execution time is consumed to prepare relevant data and software.

\subsection{the data size of the second solution:}
according to the data and software resources involved in this example, the size of each category is shown in this table.

the size of hadoop need to reconsidered. how to correctly illustrate the data size of this example?\\

\subsection{the breakdown of execution time of the third solution: }
the breakdown of execution time of the third solution is illustrated in this table. the time used to obtain file namelist and generate p1 is greatly longer than the execution time within the new package. however, the time consumption of file namelist obtainance and package generation is one-time. that is, once the package is generated, many users can directly obtain the package and re-execute it separately.

\subsection{ the data size of the third solution}
The data categories is more complex than our imagination. Except the experimental data stored in Hadoop and the software stored in CMSSW\_5\_3\_11\_patch3, files from /usr /lib /bin and other paths are also necessary for the execution of the program.\\

\subsection{ Data size comparison of 2nd and 3rd solution}
The packaging utility checks the system call of each file within the namelist, and maintains the minimum dataset, which makes the size of the final package is as small as possible. The total size of Hadoop under the second solution is astonished, while the size of Hadoop under the package is decreased to 20GB. The same trend applies to the size of CMSSW\_5\_3\_11\_patch3. Because the packaging utility tries to construct one independent and self-contained package, necessary files  from /usr, /bin, /lib are also copied into the package and denoted as “Data necessary for Package” in the table.\\

\subsection{Execution time comparison of 2nd and 3rd solution}
The time consumption of the repeat of one program from different scholars kept the same under the second solution, including software and data preparation. However, under the third solution, the data and software preparation is one-time. All the following repeat of the same program only need to obtain one copy of the package and execute the actual experimental analysis directly.\\

make use of shell packaging utility to regenerate the package to test our the packaging time and package size.\\

Another reason for the packaging utility is that not all the data and software generated by Peter’s script is used during the the actual data analysis. The packaging utility can help us find out the optimal subset of data and software involved in one actual data analysis. \\

this point is not the motivation. but one achievement comes together. out of imagination.\\

>>>>

\documentclass{article}
\usepackage{indentfirst, multicol}
\onecolumn
\begin{document}
\title{A Case Study in Preserving a High Energy Physics Application}
\author{Haiyan Meng\\ Department of Computer Science and Engineering\\ University of Notre Dame}
\date{January 2014}
\maketitle

@@

\section{First solution to repeat the program}
\indent First, Matthias introduced the general workflow of his tau analysis through one long email including notes, linux shell commands, web links.\\

@@

what’s more, step 3 of this tau analysis requires the new user owning the access authority for grid, however, granting  everyone who wants to repeat the analysis the access authority for grid (grid certificate) is too wasteful and unsafe. \\

*****lack: the email content\\

\section{second solution to repeat the program}
\indent To make the repeat of one analysis convenient and feasible, we integrate the content of all the notes, commands and web links involved in the emails into one neat, complete shell script, which begins with the definition of environment variables, then data obtainance from grid, software obtainance from cmssw, git and other web resources, and software installation, ends with the execution of the actual analysis program.\\

*****lack: the script of 2nd solution \\

@@

\section{third solution to repeat the program}
\indent the difficulty of data access authority obtainance enforces us to find out one independent solution, in which the repeat of the original analysis can be done without any external dependency. that is, one independent and self-contained package containing all the data and software dependencies is necessary.\\

parrot is a virtual filesystem access tool which attaching existing programs to a variety of remote I/O systems including http, ftp, gridftp, irods, hdfs, xrootd, grow and chirp. it traps all system calls of one program through ptrace debugging interface, and replaces them with remote I/O operations as desired. through executing one program under parrot, all the paths of files involved in this program can be recorded.\\

@@

*****lack:script of 3rd solution\\

@@

*****lack: explain the dir structure of the package:  directory ; file content + metadata; only file metadata; different process solutions\\

@@

/ /tmp/package1-4
/tmp/package1-4 /tmp/package1-4
/dev /dev
/misc /misc
/net /net
/proc /proc
/sys /sys
/var /var
/selinux /selinux\\

*****lack: re-execute process: re-execution process will redirect all the data access into the package except for data under proc sys dev selinux\\

@@

\section{fourth solution to repeat the program}
\indent To integrate the data and software from multiple analysis programs into one package, the concrete information of data and software, such as size, version, source and the number of files, need to be recorded. we also need to design one more instructive shell script format, in which the data dependencies and software dependencies can be clearly expressed and recognized. the packaging process needs to be re-organized. packaging utility needs to maintain one list of current software and data subset already stored in the package. when one user wants to generate one package, it will fork the packaging utility, the packaging utility will scan the script, get the data dependency part and software dependency part, judge whether each dependency has been inside the package, and only add the new data and software into the package, and update the package information and package retrieval information.\\

@@

*****hmeng-doubt: maybe one lightweight database like sqlite, can be used to manage the metadata of data and software. \\

*****hmeng-doubt: difficulties: for parrot, how to recognize the start and end points of one dataset or one software. because up till now, the process unit of parrot is one single file, rather one single package.\\

*****hmeng-doubt: questions: how to set the unit of parrot: file or package\\

*****lack: the 4th version of script (how to design the new script still needs consideration):\\

\section{the relationship of different solutions}
\indent The relationship of these four solutions to repeat one program is shown in Table~\ref{table:relationship}.\\

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|r|}
        \hline
        Solution ID & Data Resources & Software Resources & Operation Manual \\ \hline
        1st Solution & grid & CMSSW Git HTTP & email \\ \hline
        2nd Solution & local (HDFS) & CMSSW Git HTTP & shell script \\ \hline
        3rd Solution & independent package & independent package & shell script + packaging utility \\ \hline
        4th Solution & independent package & independent package & shell script + packaging utility \\ \hline
    \end{tabular}
    \caption{The relationship of different solutions}
    \label{table:relationship}
\end{table}

@@

*****hmeng-doubt: potential risk: different analysis programs share some common file names, but with different file contents. we should analyze the possibility of conflict: data.\\

*****hmeng-doubt: in the fourth version, let user to mark whether they change the data and software. if changed, one new package is generated to avoid data overlap and pollution. otherwise, directly starts packaging process based on the current target package. \\

\section{comparison of the 2nd solution and the 3rd solution}
\subsection{the breakdown of execution time of the second solution: }
\indent according to the Table~\ref{table:time-2nd}, about half of the total execution time is consumed to prepare relevant data and software.\\

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
    Sub-Task & Time & Percentage \\ \hline
    Software preparation from CMSSW & 15min 30s & 25.27\% \\ \hline
    Software preparation from Git & 9s & 0.24\% \\ \hline
    Software preparation from Wget & 36s & 0.98\% \\ \hline
    Environment Build - SCRAM & 13min 20s & 21.74\% \\ \hline
    Environment Build - Python & 1s & 0.03\% \\ \hline
    Data analysis & 31min 44s & 51.74\% \\ \hline
    Total & 61min 20s & 100.00\% \\ \hline
    \end{tabular}
    \caption{The breakdown of execution time of the 2nd solution}
    \label{table:time-2nd}
\end{table}

\subsection{the data size of the second solution:}
\indent according to the data and software resources involved in this example, the size of each category is shown in Table~\ref{table:datasize-2nd}.\\

\begin{table}
    \centering
    \begin{tabular}{|l|r|}
    \hline
    Data Category & Data Size \\ \hline
    Software from CMSSW & 449MB \\ \hline
    Software from Git & 61MB \\ \hline
    Software from Wget & 52MB \\ \hline
    Hadoop & 33TB \\ \hline
    Total & 33792.562GB \\ \hline
    \end{tabular}
    \caption{The data size of the 2nd solution}
    \label{table:datasize-2nd}
\end{table}

*****hmeng-doult: the size of hadoop need to reconsidered. how to correctly illustrate the data size of this example?\\

\subsection{the breakdown of execution time of the third solution: }
\indent the breakdown of execution time of the third solution is illustrated in Table~\ref{table:time-3rd}. the time used to obtain file namelist and generate p1 is greatly longer than the execution time within the new package. however, the time consumption of file namelist obtainance and package generation is one-time. that is, once the package is generated, many users can directly obtain the package and re-execute it separately.\\

\begin{table}
    \centering
    \begin{tabular}{|l|r|}
    \hline
    Sub-Task & Time \\ \hline
    Obtain file namelist & 37min 51s \\ \hline
    Generate P1 & 13min 37s \\ \hline
    Re-run the program within P1 & 13min 5s \\ \hline
    \end{tabular}
    \caption{The time breakdown of the 3rd solution}
    \label{table:time-3rd}
\end{table}

\subsection{ the data size of the third solution}
\indent The data size of the 3rd solution is shown in Table~\ref{table:datasize-3rd}. The data categories is more complex than our imagination. Except the experimental data stored in Hadoop and the software stored in CMSSW\_5\_3\_11\_patch3, files from /usr /lib /bin and other paths are also necessary for the execution of the program.\\

\begin{table}
    \centering
    \begin{tabular}{|l|r|}
    \hline
    Data Category & Data size \\ \hline
    Hadoop & 20GB \\ \hline
    CMSSW\_5\_3\_11\_patch3 & 5.2MB \\ \hline
    pscratch & 119MB \\ \hline
    usr & 60MB \\ \hline
    Others (/sbin + /tmp / + /lib + /lib64 + /var + /opt + /bin + /etc) & 28.4MB \\ \hline
    Total & 20.213GB \\ \hline
    \end{tabular}
    \caption{The data size of the 3rd solution}
    \label{table:datasize-3rd}
\end{table}

\subsection{ Data size comparison of 2nd and 3rd solution}
\indent The packaging utility checks the system call of each file within the namelist, and maintains the minimum dataset, which makes the size of the final package is as small as possible. The total size of Hadoop under the second solution is astonished, while the size of Hadoop under the package is decreased to 20GB. The same trend applies to the size of CMSSW\_5\_3\_11\_patch3. Because the packaging utility tries to construct one independent and self-contained package, necessary files  from /usr, /bin, /lib are also copied into the package and denoted as “Data necessary for Package” in the Table~\ref{table:datasize-2nd3rd}.\\

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
     Data Category & Data size of 2nd solution & Data size of 3rd solution \\ \hline
     Hadoop & 33TB = 33792GB & 20GB \\ \hline
     CMSSW\_5\_3\_11\_patch3 & 562MB & 5.2MB \\ \hline
     Data necessary for Package & 207.4MB & N/A \\ \hline
     Total & 33792.562GB & 20.213GB \\ \hline
    \end{tabular}
    \caption{Data size comparison beweeen second solution and third solution}
    \label{table:datasize-2nd3rd}
\end{table}

\subsection{Execution time comparison of 2nd and 3rd solution}
\indent Table~\ref{table:time-2nd3rd} shows the execution time comparison between the 2nd solution and the 3rd solution. The time consumption of the repeat of one program from different scholars kept the same under the second solution, including software and data preparation. However, under the third solution, the data and software preparation is one-time. All the following repeat of the same program only need to obtain one copy of the package and execute the actual experimental analysis directly.\\

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
    Task Category & execution time of 2nd solution & execution time of 3rd solution \\ \hline
    Software Acquisition & 16min 15s & N/A \\ \hline
    Environment Building & 13min 21s  & 4s \\ \hline
    Obtain file namelist & N/A & 37min 51s \\ \hline
    Generate the package & N/A & 13min 37s \\ \hline
    Actual Experimental Analysis & 31min 44s & 13min 1s \\ \hline
    Total & 61min 20s & N/A \\ \hline
    \end{tabular}
    \caption{Execution time comparison between second and third solution}
    \label{table:time-2nd3rd}
\end{table}

*****hmeng-doubt:Another reason for the packaging utility is that not all the data and software generated by Peter’s script is used during the the actual data analysis. The packaging utility can help us find out the optimal subset of data and software involved in one actual data analysis. \\
this point is not the motivation. but one achievement comes together. out of imagination.\\
